``Dr.~Tustison (UVA) presentation''

### 2016-07-18 background/people2.Rmd
ENH:  Final commit.

##  Founders:  Brian and Nick

@@

$+$ [neurodebian](http://neuro.debian.net/pkgs/ants.html), [slicer](http://www.slicer.org/), [brainsfit](https://github.com/BRAINSia/BRAINSTools), [nipype](http://nipy.sourceforge.net/nipype/), [itk](http://www.itk.org) and more ...

>>>>

<!--
##  Founders:  Brian and Nick
-->

@@

<!--
$+$ [neurodebian](http://neuro.debian.net/pkgs/ants.html), [slicer](http://www.slicer.org/), [brainsfit](https://github.com/BRAINSia/BRAINSTools), [nipype](http://nipy.sourceforge.net/nipype/), [itk](http://www.itk.org) and more ...
-->

### 2016-07-18 ibm.Rmd
ENH:  Last minute refinements.
ENH:  Final commit.

## Gender discernibility?

@@

* "*Let's incorporate N3 into ANTs!*"
-->

## N3 adoption issues

@@

## N4

@@

* tested nightly within the ITK dashboard system
-->

@@

<--
##  Atropos -- cutting the threads of fate

@@

![](./tools/atropos/figures/atroposFlow.png)
-->

@@

```bash
$ DenoiseImage --help

@@

@@

# But, wait, there's more!

<!--
##  What about using both the T1 & T2?
-->

## ANTs tools are multivariate

![](./evaluation/figures/rfRmse05ANTsT1T2.png)

## Arno-thick-in-the-head (ATITH)

_What if we made a crude estimate of the cortical thickness?_

$$thickness_{ROI} = \frac{volume_{ROI}}{area_{ROI}}$$

## Make sure you estimate the [surface area](http://www.insight-journal.org/browse/publication/852) correctly!

![](./evaluation/figures/LabelThickness.png)

<!--
----

_So how does ATITH compare with ANTs, FS?_

![](./evaluation/figures/atith.png)

## Brain constellation maps

![](./evaluation/figures/brainConstellationMaps.png)

## _Does [denoising](http://www.ncbi.nlm.nih.gov/pubmed/20027588) help?_

## Contribution from Jose

```bash
$ DenoiseImage

     -n, --noise-model (Rician)/Gaussian
          Employ a Rician or Gaussian noise model.

     --help
          Print the help menu.
```

## _Does [denoising](http://www.ncbi.nlm.nih.gov/pubmed/20027588) help?_

![](./evaluation/figures/rfRmseDenoise05.png)

## Longitudinal processing

![](./longitudinal/figures/longitudinalPipeline.png)

# But the best part is ...

## it is absolutely ``free''!

```bash
${ANTSPATH}/antsCorticalThickness.sh \
  -a IXI/T1/IXI002-Guys-0828-T1.nii.gz \
  -e IXI/template/T_template0.nii.gz \
  -m IXI/template/T_template0ProbabilityMask.nii.gz \
  -f IXI/template/T_template0ExtractionMask.nii.gz \
  -p IXI/template/Priors/priors%d.nii.gz \
  -o IXI/ANTsResults/IXI002-Guys-0828-
```

[__Data availability__](https://github.com/ntustison/KapowskiChronicles)

*  "_Hey, can I have the FreeSurfer measurements for the entorhinal cortex?_"
Sure, why not?---[Hasan, et al., J Neuroimaging](http://www.ncbi.nlm.nih.gov/pubmed/26565394)

*  "_Can I have one or more of the templates that you used for your study?_" Would you like the priors as well?

>>>>

## Gender?

@@

* "*Let's incorporate N3 into ANTs!*"

<!--
## Nonparametric nonuniform intensity normalization (N3)

@@

## N4 ("Nick's N3")

@@

* tested nightly within the ITK dashboard system

@@

     --help
          Print the help menu.
          <VALUES>: 1
```
-->

<!--
##  Atropos -- cutting the threads of fate

@@

![](./tools/atropos/figures/atroposFlow.png)

@@

![](./tools/figures/denoising.png)

<!--
```bash
$ DenoiseImage --help

@@

```
-->

@@

### 2016-07-18 ibm.tex
ENH:  Final commit.

\documentclass[ignorenonframetext,]{beamer}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
\usetheme{AnnArbor}
\usecolortheme{dolphin}
\usefonttheme{professionalfonts}
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\newif\ifbibliography
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{{#1}}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{{#1}}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{{#1}}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{{#1}}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{{#1}}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{{#1}}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
\newcommand{\ImportTok}[1]{{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{{#1}}}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{{#1}}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{{#1}}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{{#1}}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{{#1}}}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{{#1}}}}
\newcommand{\BuiltInTok}[1]{{#1}}
\newcommand{\ExtensionTok}[1]{{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{{#1}}}
\newcommand{\RegionMarkerTok}[1]{{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{{#1}}}}
\newcommand{\NormalTok}[1]{{#1}}
\usepackage{longtable,booktabs}
\usepackage{caption}
% These lines are needed to make table captions work with longtable:
\makeatletter
\def\fnum@table{\tablename~\thetable}
\makeatother
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight0.8\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}

@@

\begin{frame}{Founders: Brian and Nick}

@@

\(+\) \href{http://neuro.debian.net/pkgs/ants.html}{neurodebian},
\href{http://www.slicer.org/}{slicer},
\href{https://github.com/BRAINSia/BRAINSTools}{brainsfit},
\href{http://nipy.sourceforge.net/nipype/}{nipype},
\href{http://www.itk.org}{itk} and more \ldots{}

@@

\begin{frame}[fragile]{\texttt{antsRegistration}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{$ }\KeywordTok{antsRegistration} \NormalTok{--help}

\KeywordTok{COMMAND}\NormalTok{:}
     \KeywordTok{antsRegistration}
          \KeywordTok{This} \NormalTok{program is a user-level registration application meant to utilize}
          \KeywordTok{ITKv4-only} \NormalTok{classes. The user can specify any number of }\StringTok{"stages"} \NormalTok{where a stage}
          \KeywordTok{consists} \NormalTok{of a transform}\KeywordTok{;} \KeywordTok{an} \NormalTok{image metric}\KeywordTok{;} \KeywordTok{and} \NormalTok{iterations, shrink factors, and}
          \KeywordTok{smoothing} \NormalTok{sigmas for each level.Note that dimensionality, metric, transform,}
          \KeywordTok{output}\NormalTok{, convergence, shrink-factors and smoothing-sigmas parameters are}
          \KeywordTok{mandatory.}

\KeywordTok{OPTIONS}\NormalTok{:}
     \KeywordTok{--version}
          \KeywordTok{Get} \NormalTok{Version Information.}

     \KeywordTok{-d}\NormalTok{, --dimensionality 2/3}
          \KeywordTok{This} \NormalTok{option forces the image to be treated as a specified-dimensional image. If}
          \KeywordTok{not} \NormalTok{specified, we try to infer the dimensionality from the input image.}

     \KeywordTok{-o}\NormalTok{, --output outputTransformPrefix}
                  \NormalTok{[}\KeywordTok{outputTransformPrefix}\NormalTok{,}\KeywordTok{<}\NormalTok{outputWarpedImage}\KeywordTok{>}\NormalTok{,}\KeywordTok{<}\NormalTok{outputInverseWarpedImage}\KeywordTok{>}\NormalTok{]}
          \KeywordTok{Specify} \NormalTok{the output transform prefix (output format is .nii.gz )}\KeywordTok{.} \KeywordTok{Optionally}\NormalTok{, one}
          \KeywordTok{can} \NormalTok{choose to warp the moving image to the fixed space and, if the inverse}
          \KeywordTok{transform} \NormalTok{exists, one can also output the warped fixed image. Note that only the}
          \KeywordTok{images} \NormalTok{specified in the first metric call are warped. Use antsApplyTransforms to}
          \KeywordTok{warp} \NormalTok{other images using the resultant transform(s)}\KeywordTok{.}

     \KeywordTok{-j}\NormalTok{, --save-state saveSateAsTransform}
          \KeywordTok{Specify} \NormalTok{the output file for the current state of the registration. The state}
          \KeywordTok{file} \NormalTok{is written to an hdf5 composite file. It is specially usefull if we want to}
          \KeywordTok{save} \NormalTok{the current state of a SyN registration to the disk, so we can load and}
          \KeywordTok{restore} \NormalTok{that later to continue the next registration process directly started}
          \KeywordTok{from} \NormalTok{the last saved state. The output file of this flag is the same as the}
          \KeywordTok{write-composite-transform}\NormalTok{, unless the last transform is a SyN transform. In that}
          \KeywordTok{case}\NormalTok{, the inverse displacement field of the SyN transform is also added to the}
          \NormalTok{output composite transform. Again notice that this file cannot be treated as a}
          \NormalTok{transform, and restore-state option must be used to load the written file by}
          \NormalTok{this flag.}

     \NormalTok{-k, --restore-state restoreStateAsATransform}
          \NormalTok{Specify the initial state of the registration which get immediately used to}
          \NormalTok{directly initialize the registration process. The flag is mutually exclusive}
          \NormalTok{with other intialization flags.If this flag is used, none of the}
          \NormalTok{initial-moving-transform and initial-fixed-transform cannot be used.}

     \NormalTok{-a, --write-composite-transform 1/(0)}
          \NormalTok{Boolean specifying whether or not the composite transform (and its inverse, if}
          \NormalTok{it exists) should be written to an hdf5 composite file. This is false by default}
          \NormalTok{so that only the transform for each stage is written to file.}
          \NormalTok{<VALUES>: 0}

     \NormalTok{-p, --print-similarity-measure-interval <unsignedIntegerValue>}
          \NormalTok{Prints out the CC similarity metric measure between the full-size input fixed}
          \NormalTok{and the transformed moving images at each iteration a value of 0 (the default)}
          \NormalTok{indicates that the full scale computation should not take placeany value greater}
          \NormalTok{than 0 represents the interval of full scale metric computation.}
          \NormalTok{<VALUES>: 0}

     \NormalTok{-v, --write-interval-volumes <unsignedIntegerValue>}
          \NormalTok{Writes out the output volume at each iteration. It helps to present the}
          \NormalTok{registration process as a short movie a value of 0 (the default) indicates that}
          \NormalTok{this option should not take placeany value greater than 0 represents the}
          \NormalTok{interval between the iterations which outputs are written to the disk.}
          \NormalTok{<VALUES>: 0}

     \NormalTok{-z, --collapse-output-transforms (1)/0}
          \NormalTok{Collapse output transforms. Specifically, enabling this option combines all}
          \NormalTok{adjacent transforms wherepossible. All adjacent linear transforms are written to}
          \NormalTok{disk}\KeywordTok{ in} \NormalTok{the forman itk affine transform }\KeywordTok{(}\NormalTok{called xxxGenericAffine.mat}\KeywordTok{).}
          \KeywordTok{Similarly}\NormalTok{, all adjacent displacement field transforms are combined when written}
          \KeywordTok{to} \NormalTok{disk (e.g. xxxWarp.nii.gz and xxxInverseWarp.nii.gz (if available))}\KeywordTok{.Also}\NormalTok{, an}
          \KeywordTok{output} \NormalTok{composite transform including the collapsed transforms is written to the}
          \KeywordTok{disk} \NormalTok{(called outputCollapsed(Inverse)}\KeywordTok{Composite}\NormalTok{)}\KeywordTok{.}
          \KeywordTok{<VALUES>}\NormalTok{: 1}

     \KeywordTok{-i}\NormalTok{, --initialize-transforms-per-stage (1)}\KeywordTok{/0}
          \KeywordTok{Initialize} \NormalTok{linear transforms from the previous stage. By enabling this option,}
          \KeywordTok{the} \NormalTok{current linear stage transform is directly intialized from the previous}
          \KeywordTok{stage}\StringTok{'s linear transform; this allows multiple linear stages to be run where}
\StringTok{          each stage directly updates the estimated linear transform from the previous}
\StringTok{          stage. (e.g. Translation -> Rigid -> Affine).}
\StringTok{          <VALUES>: 0}

\StringTok{     -n, --interpolation Linear}
\StringTok{                         NearestNeighbor}
\StringTok{                         MultiLabel[<sigma=imageSpacing>,<alpha=4.0>]}
\StringTok{                         Gaussian[<sigma=imageSpacing>,<alpha=1.0>]}
\StringTok{                         BSpline[<order=3>]}
\StringTok{                         CosineWindowedSinc}
\StringTok{                         WelchWindowedSinc}
\StringTok{                         HammingWindowedSinc}
\StringTok{                         LanczosWindowedSinc}
\StringTok{          Several interpolation options are available in ITK. These have all been made}
\StringTok{          available. Currently the interpolator choice is only used to warp (and possibly}
\StringTok{          inverse warp) the final output image(s).}

\StringTok{     -g, --restrict-deformation PxQxR}
\StringTok{          This option allows the user to restrict the optimization of the displacement}
\StringTok{          field, translation, rigid or affine transform on a per-component basis. For}
\StringTok{          example, if one wants to limit the deformation or rotation of 3-D volume to the}
\StringTok{          first two dimensions, this is possible by specifying a weight vector of '}\NormalTok{1x1x0}\StringTok{'}
\StringTok{          for a deformation field or '}\NormalTok{1x1x0x1x1x0}\StringTok{' for a rigid}
\StringTok{          transformation.Low-dimensional restriction only works if there are no preceding}
\StringTok{          transformations.}

\StringTok{     -q, --initial-fixed-transform initialTransform}
\StringTok{                                   [initialTransform,<useInverse>]}
\StringTok{                                   [fixedImage,movingImage,initializationFeature]}
\StringTok{          Specify the initial fixed transform(s) which get immediately incorporated into}
\StringTok{          the composite transform. The order of the transforms is stack-esque in that the}
\StringTok{          last transform specified on the command line is the first to be applied. In}
\StringTok{          addition to initialization with ITK transforms, the user can perform an initial}
\StringTok{          translation alignment by specifying the fixed and moving images and selecting an}
\StringTok{          initialization feature. These features include using the geometric center of the}
\StringTok{          images (=0), the image intensities (=1), or the origin of the images (=2).}

\StringTok{     -r, --initial-moving-transform initialTransform}
\StringTok{                                    [initialTransform,<useInverse>]}
\StringTok{                                    [fixedImage,movingImage,initializationFeature]}
\StringTok{          Specify the initial moving transform(s) which get immediately incorporated into}
\StringTok{          the composite transform. The order of the transforms is stack-esque in that the}
\StringTok{          last transform specified on the command line is the first to be applied. In}
\StringTok{          addition to initialization with ITK transforms, the user can perform an initial}
\StringTok{          translation alignment by specifying the fixed and moving images and selecting an}
\StringTok{          initialization feature. These features include using the geometric center of the}
\StringTok{          images (=0), the image intensities (=1), or the origin of the images (=2).}

\StringTok{     -m, --metric CC[fixedImage,movingImage,metricWeight,radius,<samplingStrategy=\{None,Regular,Random\}>,<samplingPercentage=[0,1]>]}
\StringTok{                  MI[fixedImage,movingImage,metricWeight,numberOfBins,<samplingStrategy=\{None,Regular,Random\}>,<samplingPercentage=[0,1]>]}
\StringTok{                  Mattes[fixedImage,movingImage,metricWeight,numberOfBins,<samplingStrategy=\{None,Regular,Random\}>,<samplingPercentage=[0,1]>]}
\StringTok{                  MeanSquares[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy=\{None,Regular,Random\}>,<samplingPercentage=[0,1]>]}
\StringTok{                  Demons[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy=\{None,Regular,Random\}>,<samplingPercentage=[0,1]>]}
\StringTok{                  GC[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy=\{None,Regular,Random\}>,<samplingPercentage=[0,1]>]}
\StringTok{                  ICP[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>]}
\StringTok{                  PSE[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>,<pointSetSigma=1>,<kNeighborhood=50>]}
\StringTok{                  JHCT[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>,<pointSetSigma=1>,<kNeighborhood=50>,<alpha=1.1>,<useAnisotropicCovariances=1>]}
\StringTok{                  IGDM[fixedImage,movingImage,metricWeight,fixedMask,movingMask,<neighborhoodRadius=0x0>,<intensitySigma=0>,<distanceSigma=0>,<kNeighborhood=1>,<gradientSigma=1>]}
\StringTok{          These image metrics are available--- CC: ANTS neighborhood cross correlation,}
\StringTok{          MI: Mutual information, Demons: (Thirion), MeanSquares, and GC: Global}
\StringTok{          Correlation. The "metricWeight" variable is used to modulate the per stage}
\StringTok{          weighting of the metrics. The metrics can also employ a sampling strategy}
\StringTok{          defined by a sampling percentage. The sampling strategy defaults to '}\NormalTok{None}\StringTok{' (aka}
\StringTok{          a dense sampling of one sample per voxel), otherwise it defines a point set over}
\StringTok{          which to optimize the metric. The point set can be on a regular lattice or a}
\StringTok{          random lattice of points slightly perturbed to minimize aliasing artifacts.}
\StringTok{          samplingPercentage defines the fraction of points to select from the domain. In}
\StringTok{          addition, three point set metrics are available: Euclidean (ICP), Point-set}
\StringTok{          expectation (PSE), and Jensen-Havrda-Charvet-Tsallis (JHCT).}

\StringTok{     -t, --transform Rigid[gradientStep]}
\StringTok{                     Affine[gradientStep]}
\StringTok{                     CompositeAffine[gradientStep]}
\StringTok{                     Similarity[gradientStep]}
\StringTok{                     Translation[gradientStep]}
\StringTok{                     BSpline[gradientStep,meshSizeAtBaseLevel]}
\StringTok{                     GaussianDisplacementField[gradientStep,updateFieldVarianceInVoxelSpace,totalFieldVarianceInVoxelSpace]}
\StringTok{                     BSplineDisplacementField[gradientStep,updateFieldMeshSizeAtBaseLevel,totalFieldMeshSizeAtBaseLevel,<splineOrder=3>]}
\StringTok{                     TimeVaryingVelocityField[gradientStep,numberOfTimeIndices,updateFieldVarianceInVoxelSpace,updateFieldTimeVariance,totalFieldVarianceInVoxelSpace,totalFieldTimeVariance]}
\StringTok{                     TimeVaryingBSplineVelocityField[gradientStep,velocityFieldMeshSize,<numberOfTimePointSamples=4>,<splineOrder=3>]}
\StringTok{                     SyN[gradientStep,updateFieldVarianceInVoxelSpace,totalFieldVarianceInVoxelSpace]}
\StringTok{                     BSplineSyN[gradientStep,updateFieldMeshSizeAtBaseLevel,totalFieldMeshSizeAtBaseLevel,<splineOrder=3>]}
\StringTok{                     Exponential[gradientStep,updateFieldVarianceInVoxelSpace,velocityFieldVarianceInVoxelSpace,<numberOfIntegrationSteps>]}
\StringTok{                     BSplineExponential[gradientStep,updateFieldMeshSizeAtBaseLevel,velocityFieldMeshSizeAtBaseLevel,<numberOfIntegrationSteps>,<splineOrder=3>]}
\StringTok{          Several transform options are available. The gradientStep or learningRate}
\StringTok{          characterizes the gradient descent optimization and is scaled appropriately for}
\StringTok{          each transform using the shift scales estimator. Subsequent parameters are}
\StringTok{          transform-specific and can be determined from the usage. For the B-spline}
\StringTok{          transforms one can also specify the smoothing in terms of spline distance (i.e.}
\StringTok{          knot spacing).}

\StringTok{     -c, --convergence MxNxO}
\StringTok{                       [MxNxO,<convergenceThreshold=1e-6>,<convergenceWindowSize=10>]}
\StringTok{          Convergence is determined from the number of iterations per level and is}
\StringTok{          determined by fitting a line to the normalized energy profile of the last N}
\StringTok{          iterations (where N is specified by the window size) and determining the slope}
\StringTok{          which is then compared with the convergence threshold.}

\StringTok{     -s, --smoothing-sigmas MxNxO...}
\StringTok{          Specify the sigma of gaussian smoothing at each level. Units are given in terms}
\StringTok{          of voxels ('}\NormalTok{vox}\StringTok{') or physical spacing ('}\NormalTok{mm}\StringTok{'). Example usage is '}\NormalTok{4x2x1mm}\StringTok{' and}
\StringTok{          '}\NormalTok{4x2x1vox}\StringTok{' where no units implies voxel spacing.}

\StringTok{     -f, --shrink-factors MxNxO...}
\StringTok{          Specify the shrink factor for the virtual domain (typically the fixed image) at}
\StringTok{          each level.}

\StringTok{     -u, --use-histogram-matching}
\StringTok{          Histogram match the images before registration.}

\StringTok{     -l, --use-estimate-learning-rate-once}
\StringTok{          turn on the option that lets you estimate the learning rate step size only at}
\StringTok{          the beginning of each level. * useful as a second stage of fine-scale}
\StringTok{          registration.}

\StringTok{     -w, --winsorize-image-intensities [lowerQuantile,upperQuantile]}
\StringTok{          Winsorize data based on specified quantiles.}

\StringTok{     -x, --masks [fixedImageMask,movingImageMask]}
\StringTok{          Image masks to limit voxels considered by the metric.}

\StringTok{     --float}
\StringTok{          Use '}\NormalTok{float}\StringTok{' instead of '}\NormalTok{double}\StringTok{' for computations.}
\StringTok{          <VALUES>: 0}

\StringTok{     -v, --verbose (0)/1}
\StringTok{          Verbose output.}

\StringTok{     -h}
\StringTok{          Print the help menu (short version).}

\StringTok{     --help}
\StringTok{          Print the help menu. Will also print values used on the current command line}
\StringTok{          call.}
\end{Highlighting}
\end{Shaded}

@@

\begin{frame}{Gender discernibility?}

\includegraphics{./papers/figures/template5.jpg}

@@

\begin{frame}{N3 adoption issues}

\includegraphics{./tools/n4/figures/whyN4.png}

\begin{frame}{Atropos: flexible code base}

``20+ years of development. \emph{Show me the code!}''

\includegraphics{./tools/atropos/figures/atropos.png}

\begin{frame}{Atropos + N4 \(\rightarrow\) \texttt{antsAtroposN4.sh}}

\includegraphics{./tools/atropos/figures/atroposFlow.png}

\begin{frame}{\texttt{DenoiseImage} --- contribution from Jose Manjon}

\includegraphics{./tools/figures/denoising.png}

@@

\begin{frame}{Age prediction per site}

\includegraphics{./evaluation/figures/agePredictionPerSite.png}

\begin{frame}{Regional importance comparison}

\includegraphics{./evaluation/figures/antsvfreesurfer_Importance.png}

ANTs (left) vs.~FreeSurfer (right)

\begin{frame}{Regional measurements}

\includegraphics{./evaluation/figures/antsvfreesurfer_regionalPlots.png}

\section{But, wait, there's more!}\label{but-wait-theres-more}

\begin{frame}{ANTs tools are multivariate}

\includegraphics{./evaluation/figures/rfRmse05ANTsT1T2.png}

\begin{frame}{Longitudinal processing}

\includegraphics{./longitudinal/figures/longitudinalPipeline.png}

@@

\includegraphics{./competitions/figures/brats2013results2.png}

@@

\begin{frame}{Other ANTsR work}

\begin{itemize}
\item
  \href{http://www.nature.com/articles/sdata20153}{Pediatric template of
  brain perfusion}
\item
  \href{http://www.ncbi.nlm.nih.gov/pubmed/26756101}{Automated
  segmentation of chronic stroke lesions using LINDA: Lesion
  identification with neighborhood data analysis}
\item
  \href{http://www.ncbi.nlm.nih.gov/pubmed/25448483}{Eigenanatomy}
\item
  Corrective learning for segmentation refinement
\end{itemize}

>>>>

\documentclass[ignorenonframetext,]{beamer}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
\usetheme{AnnArbor}
\usecolortheme{dolphin}
\usefonttheme{professionalfonts}
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\newif\ifbibliography
\usepackage{longtable,booktabs}
\usepackage{caption}
% These lines are needed to make table captions work with longtable:
\makeatletter
\def\fnum@table{\tablename~\thetable}
\makeatother
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight0.8\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}

@@

@@

@@

@@

@@

\begin{frame}[fragile]{N4 (``Nick's N3'')}

\begin{itemize}
\item
  comparative
  \href{http://www.ncbi.nlm.nih.gov/pubmed/20378467}{evaluation}
\item
  small spline distances (useful for higher magnet strengths)
\item
  multiresolution
\item
  weighted regional mask (used in
  \href{https://github.com/stnava/ANTs/blob/master/Scripts/antsAtroposN4.sh}{\texttt{antsAtroposN4.sh}})
\item
  fast execution times
\item
  \emph{publicly available}
\item
  tested nightly within the ITK dashboard system
\end{itemize}

@@

@@

\includegraphics{./competitions/figures/brats2013results1.png}

@@
